Test CPE decomposition

### 2023-11-24 use_case/cpe_decomposition.Rmd

```{r}
data_raw <- open_dataset(here::here("res", "simCSZenrich2", "sim_toy_compensatory_dyn.arrow"),
          format = "arrow") %>%
collect() %>%
filter(!is.na(richness)) %>%
mutate(
  stoch_d = map2(species, stoch, function(bm, d_stoch) {
    .1 * bm * exp(d_stoch)
    }),
  species = map(species, ~matrix(.x, nrow = 100)),
  stoch = map(stoch, ~matrix(.x, nrow = 100)),
  stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
  cpe = map_dbl(species, compensatory_effect),
  cpe_env = map_dbl(stoch_d, compensatory_effect),
  cpe_int = cpe / cpe_env
)
```

@@

>>>>

```{r}
data_raw <- open_dataset(
  here::here("use_case", "sim_toy_compensatory_dyn.arrow"),
  format = "arrow") %>%
collect() %>%
filter(!is.na(richness)) %>%
mutate(
  stoch_d = map2(species, stoch, function(bm, d_stoch) {
    .1 * bm * exp(d_stoch)
    }),
  species = map(species, ~matrix(.x, nrow = 100)),
  stoch = map(stoch, ~matrix(.x, nrow = 100)),
  stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
  cpe = map_dbl(species, compensatory_effect),
  cpe_env = map_dbl(stoch_d, compensatory_effect),
  cpe_int = cpe / cpe_env
)
```

@@

```{r}
source(here::here("R", "plotting_methods.R"))
```

```{r}
ti <- data_raw %>%
  filter(rho == 0, Z == 10, env_stoch == .6)
nice_ts <- ti$species[[2]] %>%
  .[, colSums(.) > 0] %>%
  as_tibble() %>%
  mutate(time = 1:n()) %>%
  pivot_longer(-time, names_to = "species", values_to = "biomass")
p_nice_ts_sp <- nice_ts %>%
  ggplot(aes(y = biomass, x = time, color = species)) +
  geom_line() +
  labs(y = "Biomass", x = "Time") +
  theme_half_open() +
  theme(
    legend.position = "none",
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
ggsave_multiple(
  c("p_nice_ts_sp.png", "p_nice_ts_sp.pdf"),
  plot = p_nice_ts_sp,
  path = here::here("use_case", "figures"),
  scale = 1.5,
  dpi = 600,
  width = 88,
  height = 88 * .5,
  units = "mm"
)

sum_nice_ts <- nice_ts %>%
  group_by(time) %>%
  summarise(biomass = sum(biomass))

p_sum_nice_ts <- sum_nice_ts %>%
  ggplot(aes(y = biomass, x = time)) +
  geom_line(color = "black") +
  labs(y = "Biomass", x = "Time") +
  theme_half_open() +
  theme(
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
ggsave_multiple(
  c("p_sum_nice_ts.png", "p_sum_nice_ts.pdf"),
  plot = p_sum_nice_ts,
  path = here::here("use_case", "figures"),
  scale = 1.5,
  dpi = 600,
  width = 88,
  height = 88 * .5,
  units = "mm"
)

p_hist_biomass <- sum_nice_ts %>%
  ggplot(aes(x = biomass)) +
  geom_histogram(bins = 50, fill = "black") +
  labs(x = "Biomass", y = "") +
  theme_void() +
  theme(
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

ggsave_multiple(
  c("p_hist_biomass.png", "p_hist_biomass.pdf"),
  plot = p_hist_biomass,
  path = here::here("use_case", "figures"),
  scale = 1,
  dpi = 600,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
```
